%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}


% adjust the page margins
\usepackage[scale=0.85]{geometry}  % Return to original margin size
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt,parsep=2pt}  % More breathing room in lists

\usepackage{import}

% personal data
\name{Peyton}{Spencer}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{Denver, CO}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
 %\phone[mobile]{(+88)0 1718268856}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{peyton@omniaura.co}                               % optional, remove / comment the line if not wanted
\homepage{github.com/peyton-spencer}                         % optional, remove / comment the line if not wanted

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l@{}} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\bfseries #5}
  \end{tabular} \\[1ex]
  \begin{tabular}{@{}l@{}} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\[1ex]%
    \begin{minipage}{\textwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{2ex}}  % Increased spacing between entries

\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l@{}} 
    {\bfseries #2}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\[1ex]%
    \begin{minipage}{\textwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{3ex}}  % More space between projects

\setlength{\tabcolsep}{12pt}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
\end{tabular}
\end{center}

\section{WORK EXPERIENCE}
{\customcvproject{Arculus, Backend Software Developer}{2022 - present}
{
Senior backend developer for the Arculus cold storage wallet, focused on designing and implementing high-performance multi-chain APIs that power the platform's mobile applications. Lead backend architect responsible for system reliability, performance optimization, and blockchain integrations.
    \begin{itemize}
        \item Architected and implemented a Kubernetes-deployed Go backend that aggregates 32+ blockchains through a unified API interface, replacing a limited third-party solution while maintaining 99.9\% uptime.
        \item Designed chain-agnostic API architecture with automatic failover and hot-swapping capabilities.
        \item Created libraries to simplify rapid blockchain integrations.
        \item Optimized system performance through strategic database indexing, Redis caching, and query optimization.
        \item Fixed critical idle DB connection leaks resulting in significant RDS cost reduction.
        \item Migrated secrets from environment variables to AWS Secrets Manager.
        \item Delivered 14 major releases in 10 months with zero breaking changes, consistently meeting mobile app team deadlines and requirements.
        \item Established robust CI/CD pipelines with Github Actions for automated testing, security scanning, and deployment, improving team velocity and code quality.
        \item Led technical implementations for major blockchain ecosystems including Bitcoin, Ethereum, Solana, and Cosmos, enabling new B2B partnerships.
        \item Recognized as a blockchain technology expert, providing technical guidance to mobile teams while maintaining extensive system documentation.
    \end{itemize}
}
}

{\customcvproject{ETHDenver, Hackathon Participant }{2022, 2024}
{
    \begin{itemize}
        \item 2024: \href{https://devfolio.co/projects/oops-a44f}{"Oops!"} top 15 hackathon project and a \$5,000 prize.
        \item 2022: \href{https://github.com/teamhostel/suMERIT}{"suMERIT"} \$9,000 bounty from Metis blockchain.
    \end{itemize}
}
}

\section{EDUCATION}
{\customcventry{Fall 2016-Spring 2021}{Bachelor in Electrical Engineering   }{Auburn University}{Auburn, AL}{}{}}
GPA: 3.86, Dean's List \\ 
ACT: 34, National Merit Finalist \\
GRE: 163 Verbal, 167 Quantitative\\

\section{KEY SKILLS}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} >{\bfseries}l l}
Programming & Go, SQL, Rust, TypeScript, React, Swift, Java, Kotlin, C++\\[2ex]
Backend & AWS, GCP, Redis, Docker, Kubernetes, CI/CD, Microservices, Postgres, Sqlite \\[2ex]
Blockchain & Solidity, Ethereum, EVM, Solana \\[2ex]
Earned Airdrops & ENS, Optimism, Arbitrum, ZKSync \\[2ex]
AI & Prompt Engineering, LLMs, Claude, Gemini, Mistral, OpenAI, RAG, Agents
\end{tabular*}


\section{ENTREPRENEURSHIP}
{\customcvproject{Omni Aura LLC, Co-Founder}{2020 - present}
  {
  \begin{itemize}
    \item Spearheaded the development of Ditto, a cutting-edge AI assistant designed to revolutionize smart home control and provide personalized support for audiovisual creation, while also offering a broad array of useful tools to simplify daily life.
    \item Successfully secured \$25,000 in funding to drive the growth and development of Ditto.
    \item Collaborated with the development team to build Ditto's capabilities, including its ability to generate text, images, and 3D models, as well as its integration with various smart home devices.
    \item Led the development of Ditto's user-friendly interface, making it easy for users to access and utilize its various features, from generating creative content to controlling their smart home environment.
    \end{itemize}
  }
}

{\customcvproject{Future Trees Music, Founder}{2018 - present}
  {
  \begin{itemize}
    \item Released 34 songs recorded in home studio. Dedicated music to championing sustainability.
    \item Received an Audius grant worth over \$1,000 to host a {remix contest} with 24 entries. Created {Audius how-to videos} and onboarded 7 new artists to the platform.
    \item Collaborated with 2 artists to place intro music for the {Seed Club Podcast}. Won 1st place out of 31 entries, earning 1 ETH.
    \end{itemize}
  }
}

\end{document}


%% end of file `template.tex'.
