\documentclass[12pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.85]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=5pt,parsep=2pt}
\usepackage{import}

\name{Peyton}{Spencer}
\address{}{}{}
\email{peyton@heyditto.ai}
\homepage{github.com/peyton-spencer}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l@{}} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\bfseries #5}
  \end{tabular} \\[1ex]
  \begin{tabular}{@{}l@{}} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\[1ex]%
    \begin{minipage}{\textwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{2ex}}  % Increased spacing between entries

\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l@{}} 
    {\bfseries #2}
  \end{tabular}
  \hfill
  \begin{tabular}{r@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\[1ex]%
    \begin{minipage}{\textwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{3ex}}  % More space between projects

\setlength{\tabcolsep}{12pt}


\begin{document}
\makecvtitle
\vspace*{-25mm}

\begin{center}
\begin{tabular}{ c c c c }
\end{tabular}
\end{center}

\section{EXPERIENCE}

% MARK: - Arculus
{\customcvproject{Arculus, Lead Backend Developer}{2022 - present}
{
    \begin{itemize}
        \item Built fault-tolerant multi-chain client with minimal implementation requirements for developers, handling complex failover and retry logic while maintaining high availability across 55 blockchain networks with minimal operational overhead.
        \item Architected monitoring system consolidating 55 individual chain monitors into one endpoint, achieving 55x cost reduction in DataDog Synthetic API Testing.
        \item Diagnosed and resolved database connection leak growing to thousands of connections, reducing RDS costs and preventing dev environment failures through connection limits implementation.
        \item Simplified API integrations by creating expressive HTTP client package for nearly all common requests with productivity features like automatic curl command generation for debugging.
        \item Pioneered AI-assisted development practices company-wide, successfully pitching leadership on productivity investments while onboarding individual developers, positioning company ahead of industry adoption curve.
    \end{itemize}
    \textbf{Skills:} Go, Rust, Python, PostgreSQL, Redis, AWS, Docker, Kubernetes, DataDog, gRPC, Proxies, Ethereum, Solana, API Design, Cost Optimization, CLIs, CI/CD, Github Actions, AI-Assisted Development
}

% MARK: - Omni Aura
{\customcvproject{Omni Aura, Co-Founder}{2020 - present}
{
    \begin{itemize}
        \item Led sprint to production, implementing authentication, Stripe subscription system, and monetization strategy while migrating business logic to backend infrastructure.
        \item Streamlined product architecture by eliminating resource-intensive demo features, reducing technical debt while focusing team on memory capabilities for competitive advantage.
        \item Built agentic memory search system that recursively finds related memories then generates additional search queries from initial results to maximize relevance.
        \item Created AgentFlow, a prompt templating language and CLI.
    \end{itemize}
    \textbf{Skills:} Go, TypeScript, Python, React, SQLite, Vector Databases, GCP, Firebase, Supabase, Stripe, OAuth, OpenRouter, Agentic Pipelines, Function Calling, Structured Outputs, Prompt Engineering, Multimodal
}
}

% MARK: - Education
\section{EDUCATION}
{\customcventry{Fall 2016-Spring 2021}{Bachelor in Electrical Engineering}{Auburn University}{Auburn, AL}{}{}}
GPA: 3.86, Dean's List \\ 
ACT: 34, National Merit Finalist \\
GRE: 163 Verbal, 167 Quantitative

\end{document}
